draft_yma

### 2021-12-13 draft_yma.Rmd
marginal distribution

 **Q: do we need to convert other variables to per 1,000 population? like docs, beds, etc.**

```{r, message=FALSE}
cdi = read_csv("cdi.csv") %>%
  janitor::clean_names() %>%
  mutate(crm_1000 = 1000*(crimes/pop),
         # convert region to factors and recoded them accordingly 
         region = factor(region, levels = 1:4,
                    labels = c("northeast", "north central", "south", "west"))) %>% view()

@@

# Global
skimr::skim(cdi_descriptive) %>% 
  select(-c("skim_type","complete_rate")) %>% 
  knitr::kable(
    col.names = c("variable", "n_missing", "mean","sd","min","Q25","median","Q75","max","histogram"),
    caption = "Global Summary", digits = 2)
```

@@

```{r}
par(mfrow=c(3,5))

boxplot(cdi$area,  main = "area")
boxplot(cdi$pop, main = "pop")
boxplot(cdi$pop18, main = "pop18")
boxplot(cdi$pop65, main = "pop65")

boxplot(cdi$docs, main = "docs")
boxplot(cdi$beds, main = "beds")
boxplot(cdi$crimes, main = "crimes")
boxplot(cdi$crm_1000,  main = "crm_1000")

@@

* Here is the correlation with pairs function. More specific than the heat map above. We can observe the correlation bewteen all the terms here
```{r}
pairs(crm_1000 ~.,data=cdi_descriptive, panel = panel.smooth, upper.panel = NULL, main = "Scatterplot Matrix")
```

@@

>>>>

 **converted variables to per person and docs, beds, etc.**

```{r, message=FALSE}
cdi = read_csv("cdi.csv") %>%
  janitor::clean_names() %>%
  mutate(crm_1000 = 1000*(crimes/pop),
         pdocs = docs/pop,
         pbeds = beds/pop,
         density_pop = pop/area,
         # convert region to factors and recoded them accordingly 
         region = factor(region, levels = 1:4,
                    labels = c("northeast", "north central", "south", "west"))) %>% select(-c(docs,beds)) %>% view()

@@

# Global
skimr::skim(cdi_descriptive) %>% 
  select(-c("skim_type","complete_rate")) %>% 
    mutate(skim_variable = 
             recode(skim_variable, pcincome = "pcincome (in dollars)", totalinc = "totalinc (in million of dollars)"
  )) %>% 
  knitr::kable(
    col.names = c("variable", "n_missing", "mean","sd","min","Q25","median","Q75","max","histogram"),
    caption = "Global Summary", digits = 4)
```

@@

```{r}
par(mfrow = c(3,5))

boxplot(cdi$density_pop,  main = "density_pop")
boxplot(cdi$area, main = "area")

boxplot(cdi$pop, main = "pop")
boxplot(cdi$pop18, main = "pop18")
boxplot(cdi$pop65, main = "pop65")

boxplot(cdi$pdocs, main = "pdocs")
boxplot(cdi$pbeds, main = "pbeds")

boxplot(cdi$crm_1000,  main = "crm_1000")

@@

* Here is the correlation with pairs function. More specific than the heat map above. We can observe the correlation between all the terms here
```{r}
pairs(crm_1000 ~.,data=cdi_descriptive, panel = panel.smooth, upper.panel = NULL, main = "Scatterplot Matrix")
```

@@

```{r}
cdi %>% ggplot(aes(x = density_pop, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')

cdi %>% ggplot(aes(x = area, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')

cdi %>% ggplot(aes(x = pop, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')

cdi %>% ggplot(aes(x = pop18, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')
# positive correlation
cdi %>% ggplot(aes(x = pop65, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')

cdi %>% ggplot(aes(x = pdocs, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')

cdi %>% ggplot(aes(x = pbeds, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')

cdi %>% ggplot(aes(x = hsgrad, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red') #negative correlation

cdi %>% ggplot(aes(x = bagrad, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')

cdi %>% ggplot(aes(x = poverty, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red') # positive correlation

cdi %>% ggplot(aes(x = unemp, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')

cdi %>% ggplot(aes(x = pcincome, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')

cdi %>% ggplot(aes(x = totalinc, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')

cdi %>% ggplot(aes(x = region, y = crm_1000)) + geom_point(alpha = 0.3) + geom_smooth(method = 'lm', se = TRUE, color = 'red')
```
